\section*{Statement}
{
\noindent Tommy is a hard-working ice-cream maker. After months of tireless dedication to the craft, he manages to receive an invitation to the prestigious Australian Ice-cream Obsession Club's School of Excellence, held in the majestic land of Burgmanistan (unfortunately coinciding with those pesky informaticians). Here, students spend many hours meticulously honing their skills in the intricate art of making the perfect ice-cream.\\

\noindent Sadly, things take a turn for the worse as he miserably fails the first trial exam (strangely held before any of the lectures). Realising that he has a severe skill issue, Tommy makes it his mission to prove himself to everyone else and improve as much as he can before the final trial exam.\\

\noindent In order to get better, Tommy must attend lectures to increase his skill level in certain topics in ice-cream making (skill level in ice-cream making is denoted by a numerical score). There are $N$ different topics that are taught at camp and a total of $L$ optional lectures across various topics. The $i$th lecture lasts $h_i$ hours and improves Tommy's skill level in topic $t_i$ by $s_i$ points. However, Tommy is only human and so, he is only able to attend a total of $H$ hours of lectures before getting burnt out.\\

\noindent Additionally, in order to attend a lecture that covers a certain topic, he must have attended all previous lectures covering that topic to ensure that he understands the content of the lecture. For example, Tommy may only attend Double Scoops (DS) III if he has attended DS I and II. His total improvement at the end is the sum of his improvements in each individual topic.\\

\noindent Despite disliking informatics, Tommy is desperate and decides that it is best to ask you, an informatics student, to write a program to determine the greatest possible improvement he can make.
}