\documentclass{article}
\usepackage{multicol}
\usepackage[utf8]{inputenc}
\usepackage[textwidth=460pt, voffset=0pt]{geometry}
\usepackage{fancyhdr}
\begin{document}
\title{\vspace{-5ex}Ice-cream Obsession 3}
\author{\vspace{-5ex}}
\date{\vspace{-5ex}}
\pagestyle{fancy}
\fancyhf{}
\lhead{ACIO 2023 Contest 1}
\rfoot{Page \thepage}

\begin{center}
\huge{Ice-cream Obsession 3}\small\\
\vspace{5ex}
\begin{tabular}{|c|c|} 
\hline
Time Limit & Memory Limit \\
\hline
1 second & 128 MB \\

\hline
\end{tabular}
\end{center}
\section*{Statement}

A person has been found unconscious at an ice cream tasting event after suffering acute brain freeze.

You are the driver of the ambulance rushing this person to hospital. The country has $N$ cities (numbered 1 to $N$) and $M$ bidirectional roads between them of varying length. You are currently at city 1. You aren't going to make it to the hospital at city $N$ in time, but you have a trick up your sleeve.

Using your portal gun, you can teleport from a city to any neighbouring city you can get to by road, effectively reducing the distance of that road to zero. However, you can only use your portal gun once.

With your portal gun powers, what is the minimum distance you need to travel by road to get from city 1 to city $N$?

\section*{Input}

\begin{itemize}
\item The first line of input contains the integers $N$ and $M$.
\item The next $M$ lines contain three integers: $a$, $b$, $w$, meaning there is a bidirectional road from city $a$ to $b$ of length $w$ metres.
\end{itemize}

\section*{Output}

Output a single integer; the shortest path length.

\begin{multicols}{2}
\section*{Sample Input 1}
{\tt
5 5\\
1 2 1\\
1 3 2\\
2 4 2\\
3 4 3\\
4 5 1
}
\columnbreak
\section*{Sample Output 1}
{\tt
2
}
\end{multicols}
\section*{Constraints}
\begin{itemize}
\item $1\leq N \leq 10^5$
\item $1 \leq M \leq 2 \times 10^5$
\item $1 \le w \le 10^4$
\item You are guaranteed a path exists from 1 to $N$.
\item There are no self-edges and at most one road goes from $a$ to $b$ for any cities $a$, $b$.
\end{itemize}

\section*{Subtasks}
\begin{tabular}{l*{6}{c}r}
Number & Points & Other constraints\\
\hline
1 & 30 & $N \le 1000$\\
2 & 10 & $w = 1$ for all edges\\
3 & 60 & No other constraints
\end{tabular}
\end{document}
